Application of Generalized Additive Models for long-term and seasonal trend analysis of water quality: South San Francisco Bay case study

### 2020-06-01 manu_draft.Rmd
p vals to mod summary table

```{r modprftab, tab.cap = "Model performance statistics for each station and GAM structure (Table \\@ref(tab:modsumtab)).  Four GAMs were fit to each station and performance is summarized as $\\Delta$ AIC (from `gam0`), GCV, and R-squared values.  Models with the lowest AIC, GCV and highest R-squared values for each station are emphasized."}
totab <- modprf %>% 
  group_by(station) %>% 
  mutate(
    AIC = AIC - max(AIC),
    minaic = AIC == min(AIC), 
    mingcv = GCV == min(GCV),
    maxr2 = R2 == max(R2)
  ) %>% 
  ungroup

>>>>

```{r modprftab, tab.cap = 'Model performance statistics for each station and GAM structure (Table \\@ref(tab:modsumtab)).  Four GAMs were fit to each station and performance is summarized as $\\Delta$ AIC (from `gam0`), GCV, and R-squared values.  Models with the lowest AIC, GCV and highest R-squared values for each station are emphasized. Probability values ("P-value") show the results of Analysis of Variance comparisons between all models at a station.  The p-value for a row refers to the comparison of the model in the current row to the one preceeding.  Values indicate ns for not significantly different at $\\alpha = 0.05$, * $p< 0.05$, and ** $p < 0.005$.'}
totab <- modprf %>% 
  group_by(station) %>% 
  mutate(
    AIC = AIC - max(AIC),
    minaic = AIC == min(AIC), 
    mingcv = GCV == min(GCV),
    maxr2 = R2 == max(R2)
  ) %>% 
  ungroup
